\documentclass[12pt, letterpaper]{memoir}
\usepackage{ExamStyle}

\begin{document}
	\mainmatter
	
	\begin{center}
		{\Huge CHEM 1210}
		{\LARGE-- Fall 2016
		
		Midterm Exam 4 Study Guide (Ch. 9-11)}
	\end{center}
	
	This study guide is meant to provide only the barest direction as you study. Try to find practice problems from the textbook (both in the chapter text and in the end-of-chapter questions) rather than just relying on this guide. Note that tables and equations will not be provided here or on the exam. You can find them in your textbook. As the exam gets closer (i.e. after I write it) I will provide you with an example of the tables and equations (if any) which will be provided.	

	\subsection*{Chapter 9 -- Molecular Geometry and Bonding Theories}
	\begin{itemize}
		\item VSEPR theory
		\item Electron domain geometries
		\item Molecular geometries
		\item Seriously, memorize all of the molecular geometries
		\item Hybridization and molecular geometries
		\item Covalent bonds as electron orbital ovelap
		\begin{itemize}
			\item Theory -- why should shared electrons lead to a bond
			\item structure of σ and π bonds
			\item What types of orbitals overlap in a given bond
		\end{itemize}
		\item π bonding networks and resonance
		\item Molecular orbital theory
		\begin{itemize}
			\item Basis of MO theory -- Mixing atomic orbitals 
			\item Bonding and antibonding orbitals
			\item Ordering molecular orbitals according to energy
			\item Diamagnetism and paramagnetism
		\end{itemize}
	\end{itemize}
	
	\subsection*{Chapter 10 -- Gases}
	\begin{itemize}
		\item Measuring and converting pressures
		\item Gas laws
		\begin{itemize}
			\item Charles's Law
			\item Boyle's Law
			\item Ideal Gas Law
		\end{itemize}
		\item Density and the ideal gas law
		\item Law of partial pressures
		\item Vapor pressure and how it affects volumes measured over water
		\item Kinetic molecular theory of gases
		\begin{itemize}
			\item Average energy and velocity of gas molecules
			\item Rules governing rates of effusion and diffusion
		\end{itemize}
		\item Real gases and the Van Der Waals equation
	\end{itemize}

	\subsection*{Chapter 11 --  Intermolecular Forces}
	{\Large Note that we may not cover this material. It will depend on the pace over this next week.}
	\begin{itemize}
		\item Molecular model for states of matter -- attractive forces determine the phase
		\item Intermolecular forces
		\begin{itemize}
			\item London Dispersion forces
			\item Dipole-dipole forces
			\item Ion-dipole forces
			\item Hydrogen bonds -- how to predict them and how they work
		\end{itemize}
		\item Trends in boiling and melting points
	\end{itemize}
\end{document}